Toronto’s Shelter System Under Pressure: Investigating Homelessness and Bed Occupancy

### 2024-09-27 paper/paper.qmd
changing title

---
title: "Analyzing Homelessness and Shelter Use in Toronto: A Data-Driven Approach"
subtitle: "Understanding the Dynamics of Homelessness in Toronto through Data"
author:
  - "Tim Chen"
thanks: "Code and data are available at: https://github.com/timchen0326/toronto-shelter-data."
date: today
date-format: long
abstract: "This paper examines homelessness and shelter usage in Toronto by analyzing daily shelter occupancy data from the City of Toronto. Using data from 2021 to 2024, the analysis highlights key trends in shelter occupancy rates, bed capacity, and service user counts, broken down by program model and demographic sector. The results reveal a consistently high occupancy rate of beds, suggesting shelters are near capacity, with a growing demand for emergency services. Seasonal fluctuations in shelter usage, particularly during the winter months, point to the critical need for enhanced shelter services during extreme weather conditions. The analysis further uncovers disparities between emergency and transitional shelter capacities, emphasizing the necessity for targeted government policies to address the rising homelessness crisis. This paper aims to provide a deeper understanding of homelessness trends in Toronto and highlights the importance of data-driven solutions in addressing this ongoing social challenge."
format: 
  pdf:
    toc: true
    toc-depth: 2    
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Toronto’s Shelter System Under Pressure: Investigating Homelessness and Bed Occupancy"
subtitle: "Understanding the Dynamics of Homelessness in Toronto through Data"
author:
  - "Tim Chen"
thanks: "Code and data are available at: https://github.com/timchen0326/toronto-shelter-data."
date: today
date-format: long
abstract: "This paper examines homelessness and shelter usage in Toronto by analyzing daily shelter occupancy data from the City of Toronto. Using data from 2021 to 2024, the analysis highlights key trends in shelter occupancy rates, bed capacity, and service user counts, broken down by program model and demographic sector. The results reveal a consistently high occupancy rate of beds, suggesting shelters are near capacity, with a growing demand for emergency services. Seasonal fluctuations in shelter usage, particularly during the winter months, point to the critical need for enhanced shelter services during extreme weather conditions. The analysis further uncovers disparities between emergency and transitional shelter capacities, emphasizing the necessity for targeted government policies to address the rising homelessness crisis. This paper aims to provide a deeper understanding of homelessness trends in Toronto and highlights the importance of data-driven solutions in addressing this ongoing social challenge."
format: 
  pdf:
    toc: true
    toc-depth: 2    
number-sections: true
bibliography: references.bib
---
